Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-15 paper/current/main.tex
edit method part

where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations. There are two popular forms of the $f(r_{ij})$. The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij}  (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} (\beta > 0)$ \autocite{chen2015distance}.  $f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.

@@

%
% SUBSECTION: SEMAXIS
%
\subsection*{SemAxis}
SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
Each axis is an antonym pair defined for each specific use case.
In the case of language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.

Given vectors representing the positive and negative poles of an axis, $v^{+}$ and $v^{-}$, the axis is defined as.$v_{\text{axis}} = v^{+} - v^{-}$. For each organization in the embedding space, $w$, a score is calculated relating the term to to the positive, $v^{+}$ or negative, $v^{-}$ pole, calculated as the cosine similarity of the organization's vector with the axis,

$$
score(w)v_{\text{axis}} = \cos(u_{w}, v_{\text{axis}})
$$

>>>>

where $m_{i}$ and $m_{j}$ are the organization masses, or the yearly-average count of unique authors affiliated with each organization during the time window, and $f(r_{ij})$ is a distance-decaying function  between the two organizations. There are two popular forms of the $f(r_{ij})$. The first one is power-law function with $f(r_{ij})= r^{-\alpha}_{ij} \ (\alpha > 0)$, and the another one is exponential function with $f(r_{ij}) = e^{-\beta r_{ij}} \ (\beta > 0)$ \autocite{chen2015distance}.  $f(r_{ij})$, $C$ can be chosen as to fit the data with the simple regression.

@@

%
% SUBSECTION: SEMAXIS
%
\subsection*{SemAxis}
SemAxis~\autocite{an2018semaxis} is a technique that leverages the latent semantic characteristics of word embeddings to represent the position of terms along a conceptual axis, reflecting the relationship of these term to the concept.
Each axis is an antonym pair defined for each specific use case.
In the case of natural language, the poles of the axis could be ``good'' and ``bad'', ``surprising'' and ``unsurprising'', or ``masculine'' and ``feminine''. 
By treating organizations analogously to words and trajectories analogously to sentences, we can use SemAxis to leverage the semantic properties of the resulting embedding vectors to operationalize abstract relationships between organizations.

Let $S^+ = \{v_1^+, v_2^+ \cdots v_n^+\}$ and $S^- =\{v_1^-, v_2^- \cdots v_n^-\}$ be the sets of positive and negative poles organization vector respectively. Then, the average vectors of each set can be calculated as $V^{+} = \frac{1}{n}\sum^n_1 v_i^+$ and $V^{-} = \frac{1}{n}\sum^n_1 v_i^-$. From these average vectors of each set of poles, the semantic axis is defined as $V_{\text{axis}} = V^{+} - V^{-}$. Then,  a score of organization $w$ is calculated calculated as the cosine similarity of the organization's vector with the axis,

$$
score(w)_{V_{\text{axis}}} = \cos(u_{w}, V_{\text{axis}}) = \frac{u_{w} \cdot V_{\text{axis}}}{\lVert v_{i} \rVert \lVert V_{\text{axis}} \rVert},
$$

where higher scores means that organization $w$ is more closely aligned to $S^+$ than $S^-$.
